\large{\bf Looking forwards and backwards through locally regulated populations }

### 2022-04-27 forwards-and-backwards.tex
figure

\begin{figure}
    \begin{center}
        FIGURE
    \end{center}
    \caption{
        TODO: Figure depicting deterministic vs superprocess dichotomy:
        showing 2D images of populations,
        one with $\theta/N$ not small, the other with $\theta/N$ small.
        \label{fig:super_vs_det_2d}
    }
\end{figure}

>>>>

\begin{figure}
    \begin{center}
        \includegraphics{figures/ex1a/fkpp_123.locations}
        \includegraphics{figures/ex1b/fkpp_123.locations}
    \end{center}
    \caption{
        Snapshots of two simulations, with small $\theta$ (left) and large $\theta$ (right).
        Simulations are run with a FKPP-like parameterization:
        birth and establishment are constant, while death increases linearly with density,
        at slope $1/\theta$.
        Left: $\theta=1$. Right: $\theta=100$.
        Other parameters were the same:
        dispersal and interactions distance were set to 1,
        and the equilibrium density is 10 individuals per unit area.
        \label{fig:super_vs_det_2d}
    }
\end{figure}
